Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-06 paper-1/manuscript.tex
Typo

Finally, given the very clear contrast in $D^A$ in the sample network, we considered the possibility that, in the context of the full model, STD could also evoke global suppression in the \msc{} sequence, contrary to our stated hypothesis. If so, we should expect to see less $D^A$ in \dev{} than \msc{}. To confirm this, we analysed the contrast (\dev{} - \msc{}) in $D^A$ across networks and stimuli, and found its network median to be robustly negative (T = 955, p = 1.23e-12; one-sided Wilcoxon, n = 120), as can be seen in the inset histogram in Figure \ref{fig8}c. Taken together, we cautiously conclude that, while there is clear evidence for greater global suppression in \msc{} than \dev{} in terms of $D$, this difference appears to manifest only weakly in activity differences.

>>>>

Finally, given the very clear contrast in $D^A$ in the sample network, we considered the possibility that, in the context of the full model, STD could also evoke global suppression in the \msc{} sequence, contrary to our stated hypothesis. If so, we should expect to see less $D^A$ in \dev{} than \msc{}. To confirm this, we analyzed the contrast (\dev{} - \msc{}) in $D^A$ across networks and stimuli, and found its network median to be robustly negative (T = 955, p = 1.23e-12; one-sided Wilcoxon, n = 120), as can be seen in the inset histogram in Figure \ref{fig8}c. Taken together, we cautiously conclude that, while there is clear evidence for greater global suppression in \msc{} than \dev{} in terms of $D$, this difference appears to manifest only weakly in activity differences.
